Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-05-12 doc/paper.tex
update paper draft

{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS). This model predict the simplification that mixing angles and the CP phase are functions of two model parameters $\theta_\nu$ and $\phi_\nu$,
\begin{align}
\sin^2\theta_{12}&=\frac{1}{2-\sin2\theta_{\nu}\cos\phi_\nu},\nonumber\\
\sin^2\theta_{13}&=\frac{1}{3}(1+\sin2\theta_\nu\cos\phi_\nu),\nonumber\\
\sin^2\theta_{23}&=\frac{1-\sin2\theta_\nu\sin(\pi/6-\phi_\nu)}{2-\sin2\theta_\nu\cos\phi_\nu},\nonumber\\
J_{CP}&=-\frac{1}{6\sqrt{3}}\cos2\theta_\nu.
\end{align}
The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in Fig.
}

>>>>

\begin{figure}[!h]
 %\flushleft
 \centering
\hspace{15mm}\includegraphics[width=0.5\textwidth]{figs/theta_phi.pdf}
 \caption{\label{fig:theta_phi} {\color{red}[formate will be further tuned]}}
\end{figure}

{\color{red}To show the generality of \textbf{FaSE-GLoBES}, we present the similar result with another model -- \textit{the warped flavor symmetry} (WFS). This model predict the simplification that mixing angles and the CP phase are functions of two model parameters $\theta_\nu$ and $\phi_\nu$,
\begin{align}
\sin^2\theta_{12}&=\frac{1}{2-\sin2\theta_{\nu}\cos\phi_\nu},\nonumber\\
\sin^2\theta_{13}&=\frac{1}{3}(1+\sin2\theta_\nu\cos\phi_\nu),\nonumber\\
\sin^2\theta_{23}&=\frac{1-\sin2\theta_\nu\sin(\pi/6-\phi_\nu)}{2-\sin2\theta_\nu\cos\phi_\nu},\nonumber\\
J_{CP}&=-\frac{1}{6\sqrt{3}}\cos2\theta_\nu.
\end{align}
The constraint of $\theta_\nu$ and $\phi_\nu$ is presented in Fig~\ref{fig:theta_phi}, in which we use the best fit of NUFIT 4.0 result as the true values ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
